### 2016-05-18 rscripts/location_clusters.Rmd
make targets for processed samples

```{r, echo=F}
process_hour_rle <- function(prefix) {
  hrsind <- 0:23
  nms <- sapply(hrsind, function(h) sprintf("%s_hr_%.2d", prefix, h))
  function(hrrle) with(hrrle, {
    missing <- hrsind[!(hrsind %in% values)]
    res <- c(lengths, rep.int(0, length(missing)))[order(c(values, missing))] / sum(lengths)
    names(res) <- nms
    res
  })
}

day.abb <- c("Sun", "Mon", "Tues", "Wed","Thurs","Fri","Sat")

@@

@@

  return(c(list(
      log10_lifetime = log10(life),
      log10_total_duration = log10(total_login_time),
      log10_unique_users = log10(user_count),
      ave_duration = mean(duration), sd_duration = sd(duration)
    ),
    weekday_percent, monthly_percent, hourly_percent,
    as.list(dur_quantiles), as.list(login_hours), as.list(logout_hours)
  ))
})
digestor <- function(dt, preds, training, cache = "../input/initPred.RData") {
  { if (!file.exists(cache)) {
    d <- dt[, preds(.SD), by=location_id]
    saveRDS(d, cache)
    d
  } else {
    readRDS(cache)
  } } -> ref

>>>>

```{r, echo=F}
day.abb <- c("Sun", "Mon", "Tues", "Wed","Thurs","Fri","Sat")

@@

process_hour_rle <- function(prefix) {
  hrsind <- 0:23
  nms <- sapply(hrsind, function(h) sprintf("%s_hr_%.2d", prefix, h))
  function(hrrle) with(hrrle, {
    missing <- hrsind[!(hrsind %in% values)]
    res <- c(lengths, rep.int(0, length(missing)))[order(c(values, missing))] / sum(lengths)
    names(res) <- nms
    res
  })
}

@@

  return(c(list(
      log10_lifetime = log10(life),
      log10_total_duration = log10(total_login_time),
      log10_unique_users = log10(user_count),
      ave_duration = mean(duration), sd_duration = sd(duration)
    ),
    weekday_percent, monthly_percent, hourly_percent,
    as.list(dur_quantiles), as.list(login_hours), as.list(logout_hours)
  ))
})

digestor <- function(dt, preds, training, cache = "../input/initPred.RData") {
  { if (!file.exists(cache)) {
    d <- dt[, preds(.SD), by=location_id]
    saveRDS(d, cache)
    d
  } else {
    readRDS(cache)
  } } -> ref
